---
title: "P8105_hw5_hm2900"
output: github_document
---

```{r setup, include = FALSE, message = FALSE, warning=FALSE}
library(tidyverse)
library(rvest)

knitr::opts_chunk$set(
  echo = TRUE,
  warning = FALSE,
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_color_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

## Problem 2

Describe the raw data. Create a `city_state` variable, and then summarize within cities to obtain the total number of homicides and the number of unsolved homicides.

```{r message = FALSE}
homicide_df = 
  read_csv("./data/homicide-data.csv", na = c("", "Unknown")) %>%
  mutate(
    city_state = str_c(city, ", ", state),
    resolution = case_when(
      disposition == "Closed without arrest" ~ "unsolved", 
      disposition == "Open/No arrest" ~ "unsolved",
      disposition == "Closed by arrest" ~ "solved"
    )
  ) %>%
  relocate(city_state) %>%
  filter(city_state != "Tulsa, AL")

distinct_city = 
  homicide_df %>%
  distinct(city_state)

cities_df = homicide_df %>%
  group_by(city_state) %>%
  summarize(
    unsolved = sum(resolution == "unsolved"),
    total = n()
  )

cities_df
```
The data contains `r nrow(homicide_df)` criminal homicides over the past decade in `r nrow(distinct_city)` of the largest American cities. The data included the location of the killing, reported date, basic information of the victim (name, race, age, sex), whether an arrest was made and, in most cases, basic demographic information about each victim.

For the city of Baltimore, MD, estimate the proportion of homicides that are unsolved.

```{r message = FALSE}
baltimore_md_df = 
  homicide_df %>%
  filter(city_state == "Baltimore, MD")

baltimore_md_summary = 
  baltimore_md_df %>%
  summarize(
    unsolved = sum(resolution == "unsolved"),
    total = n()
  )

baltimore_md_test = 
  prop.test(
    x = baltimore_md_summary %>% pull(unsolved),
    n = baltimore_md_summary %>% pull(total)
  ) %>%
  broom::tidy() %>%
  select(estimate, conf.low, conf.high)

baltimore_md_test
```


Now run prop.test for each of the cities in your dataset, and extract both the proportion of unsolved homicides and the confidence interval for each.

```{r message = FALSE}
all_df = 
  cities_df %>%
  mutate(
    test_results = map2(unsolved, total, prop.test),
    tidy_results = map(test_results, broom::tidy)
  ) %>%
  select(city_state, tidy_results) %>%
  unnest(tidy_results) %>%
  select(city_state, estimate, conf.low, conf.high)

all_df
```


Create a plot that shows the estimates and CIs for each city – check out geom_errorbar for a way to add error bars based on the upper and lower limits. Organize cities according to the proportion of unsolved homicides.

```{r}
all_df %>%
  mutate(city_state = fct_reorder(city_state, estimate)) %>%
  ggplot(aes(x = city_state, y = estimate)) +
  geom_point() +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high)) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1))
```







